Chlorophylla

### 2019-08-02 Chlorophyll.Rmd
update

chloro_match %>%
  filter(date == max(date)) %>%
  ggplot(aes(x = lon, y = lat)) +
  geom_raster(aes(fill = chloro))

combined_chloro_sites <- chloro_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat")) %>% 
  dplyr::mutate(date = as.Date(date))

# Save the complete dataset
# save(combined_chloro_sites, file = "Data/combined_chloro_sites.RData")

Chloro_plot_complete <- ggplot(combined_chloro_sites, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~site, ncol = 1)
Chloro_plot_complete

# Plotting only years 2014-2015
daily_chloro_data_tester <- combined_chloro_sites %>% 
  filter(year(date) %in% seq(2014, 2015))

Chloro_ggplot(daily_chloro_data_tester, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~site, ncol = 1)
Chloro_plot_filtered

# # With the chloro pixels filter, it is now faster to create the daily data
daily_chloro_data <-  %>%
  dplyr::mutate(date = as.Date(date)) %>%
  dplyr::group_by(combi, lon, lat, date) %>%
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
  dplyr::group_by(combi, lon, lat) %>%
  tidyr::nest() %>%
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                     climatologyPeriod = c("2002-07-13", "2018-12-04"), 
                     maxPadLength = 8)) %>% 
  dplyr::select(-data) %>%
  tidyr::unnest() %>%
  select(-doy, -seas, -thresh)

## Plotting daily data
# ggplot(daily_chloro_data, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~combi, ncol = 1)

# daily_chloro_match_sites <- daily_chloro_data %>%
# left_join(pixel_match, by = c("combi", "lon", "lat", "month", "day", "year"))
```

>>>>

# chloro_match %>%
#   filter(date == max(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = chloro))
# 
# chloro_sites <- chloro_match %>%
#   left_join(pixel_match, by = c("combi", "lon", "lat")) %>% 
#   dplyr::mutate(date = as.Date(date))
# # save(chloro_sites, file = "Data_P1/chloro_sites.RData")
# 
# # Visualisation
# load("Data_P1/chloro_sites.RData")
# Chloro_plot_complete <- ggplot(chloro_sites, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~site, ncol = 1)
# Chloro_plot_complete
# 
# # Study period from 2010 - 2014
# chloro_data <- chloro_sites %>% 
#   filter(year(date) %in% seq(2010, 2014))
# # save(chloro_data, file = "Data_P1/chloro_data.RData")
# 
# # Plotting only years 2014-2015
# load("Data_P1/chloro_data.RData")
# Chloro_plot_filtered <- ggplot(chloro_data, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~site, ncol = 1)
# Chloro_plot_filtered

# Creating daily temperatures
load("Data_P1/chloro_data.RData") # Loading in the chlorophyll-a data

daily_chloro <- chloro_data %>%
  # dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(combi, lon, lat, date) %>%
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
  dplyr::group_by(combi, lon, lat) %>% 
  drop_na() %>% 
  tidyr::nest() %>%
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                     climatologyPeriod = c("2010-02-11", "2014-12-20"),
                     maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>%
  tidyr::unnest() %>%
  select(-doy, -seas, -thresh)

****Error: Evaluation error: sort(): detected NaN.*** 
```
